An Analysis of the SPDY Protocol as a Candidate for HTTP/2.0

### 2012-12-18 paper/paper.tex
Tom's work

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Asset Characterization}
\label{sec:assets}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SPDY Combination Strategy}
SPDY's most complex new feature is the ability to multiplex requests for assets
over a single TCP connection. In this way, a web page's assets can benefit from
a warmed-up TCP connection which is not subject to the TCP slow start
algorithm. Since SPDY is currently built atop SSL, SPDY can only combine assets
with a mutually-agreeable SSL certificate.

% we measure two approaches: splitting on SSL cert and IP and simply splitting
% on SSL cert (as an upper bound for combination). The first method, ssl + ip,
% is prone to some error due to the use of CDNs confusing our scraping of
% assets.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Asset Characterization}
\label{sec:assets}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{SPDY Combination Strategy}
SPDY's most complex new feature is the ability to multiplex requests for assets
over a single TCP connection. In this way, a web page's assets can benefit from
a warmed-up TCP connection which is not subject to the TCP slow start
algorithm. Since SPDY is currently built atop SSL, SPDY can only combine assets
with a mutually-agreeable SSL certificate. The assets will be combined into
separate streams over the same TCP connection, thus ideally obtaining complete
utilization of the connection and the benefit from TCP's eventual discovery of
an accurate congestion window.

In order to measure the efficiency of SPDY's asset combination, we must
determine the benefit of combining assets. The authors of SPDY claim that the
main benefit from asset combination is the reduction of network connections
required~\cite{spdy-whitepaper}. Although the HTTP/1.1 specification allows for
up to two simultaneous connections to servers, modern browsers willfully
violate it in service of page load speed and will happily open up to six
connections to each host. Websites have also been pushing the limits by
creating semantically equivalent hostnames (i.e. assets1.example.com,
assets2.example.com, etc.) for different asset servers so browsers will open
six connections to each. Thus, browsers may wind up opening hundreds of
connections immediately upon loading a page.

SPDY's asset combination addresses this. In this section we will measure the
difference in the number of connections required to load each page under two
different assumptions: first that site owners could combine all assets with
mutually-agreeable SSL certificates into one SPDY connection and second that
site owners would combine all assets served by the same IP address \textit{and}
with mutually-agreeable SSL certificates into one SPDY connection. Logically,
the first method is an upper bound for the number of connections we can save,
we estimate that the second method is more accurate for most websites but is a
lower bound for websites which employ CDNs or asset host sharding.

\subsection{SSL-only Asset Combination}
\begin{figure}[h!]
\includegraphics[width=0.4\textwidth,angle=270]{plots/asset_combination_only_ssl_ratio.eps}
\caption{Connection Ratio -- SSL-only Combination Strategy}
\label{fig:combination-ssl}
\end{figure}
The results in Figure \ref{fig:combination-ssl} assume that all assets
described by a mutually-compatible SSL certificate are combined into one SPDY
connection. Two assets have \textit{mutually-compatible} SSL certificates if
their SSL certificates are valid for the host of the other asset (with either
the Canonical Name or the Alternative Hostnames). In this way, we
systematically combine assets by adding them to the largest group with which
they are compatible. We then compare the number of asset groups (SPDY
connections) with the number of assets (HTTP connections). The CDF of the ratio
for the Alexa top 100,000 websites is plotted.

\subsection{SSL-and-IP Asset Combination}
\begin{figure}[h!]
\includegraphics[width=0.4\textwidth,angle=270]{plots/asset_combination_ssl_and_ip_ratio.eps}
\caption{Connection Ratio -- SSL-and-IP Combination Strategy}
\label{fig:combination-ssl-and-ip}
\end{figure}
The results in Figure \ref{fig:combination-ssl-and-ip} assume that all assets
described by a mutually-compatible SSL certificate and that are downloaded from
the same IP in practice are combined into one SPDY connection.
\subsection{Connection Sizes}
% we measure two approaches: splitting on SSL cert and IP and simply splitting
% on SSL cert (as an upper bound for combination). The first method, ssl + ip,
% is prone to some error due to the use of CDNs confusing our scraping of
% assets.
